Storing messages with multipartite neural cliques

### 2014-07-10 Articles/article.tex
...

		\subsubsection{The "$a$ winners take all" rule}

		To fully exploit the local regularity of the code (constant weight of $a$), we make a small modification the classic retrieving rule	by keeping activated all neurons that achieve a score equal or greater than the score appearing in $w$-th position in the ordered array of scores (where $w$ is a positive integer parameter)

@@

		\begin{algorithmic}[1]
		\Require{$v$ a binary array of length $n = c\cdot l$, $W$ the weight matrix representing the network}
		\Procedure{Sum of sum}{$v, W, \gamma, S, w$}
		%\Statex
		\For{$s$ from $1$ to S}
		\State $s \gets \gamma v + W v$
		\For{$i$ from $1$ to $c$}
			\Let{treshold}{Select(s[$i$], $w$)} \Comment{Select(t, w) returns the element that would be in rank $w$ if the array t was sorted}
			\For{$j$ from $1$ to $l$}
			\Let{$v[i][j]$}{$s[i][j]$ $\ge$ treshold}
			\EndFor
		\EndFor
		\EndFor
		%\State\Return v
		\EndProcedure
		\end{algorithmic}
		\end{algorithm}

@@

	As information is shared accross connections with multiple activated neurons per cluster, they are more resilient to network damages.

	%Marche mieux pour des bruits importants

	$P(n_{v_c} = n_0 + \gamma ) = {a (c_k-1) \choose n_0} (1-\psi)^{n_0} \psi ^ { a (c_k-1) - n_0 }$

	$P(n_{v_c} = n_0) = {a c_k \choose n_0} (1-\psi)^{n_0} \psi ^ { a c_k - n_0 }$

@@

	\begin{figure}

@@

	\section{Maximum theoretical efficiency}
		It was shown in \cite{oo}, asymptotic capacities of clique networks is $\log 2$. We generalise this result to multipartite cliques.
		The entropy of the messages set can be approximated as $H(M) \approx m c \log_2 {l \choose a}$. From $d = 1 - \left (1- \left(\frac{a}{l}\right)^2 \right)^m$, we can deduce $m \sim \frac{\log_2(1-d)}{\log_2(1-(\frac{a}{l})^2)} \sim - \frac{l^2 \log_2(1-d) \log 2}{a^2}$.
		We set $\log_2 {l \choose a} = k c$ (otherwise density approaches $0$ or $1$, and efficiency $0$). It follows that $\eta \sim c \log_2 {l \choose a} \log2(1-d) \sim \frac{k c^2 \log_2(1-d)\log 2}{a^2 {c \choose 2}}$.

@@

	\nocite{*}
	\bibliographystyle{plain} % Le style est mis entre crochets.
         \bibliography{bibli}
\end{document}

>>>>

		\subsubsection{The "$w$-winners take all" rule}

		To fully exploit the local regularity of the code (constant weight of $w$), we make a small modification the classic retrieving rule	by keeping activated all neurons that achieve a score equal or greater than the score appearing in $w$-th position in the ordered array of scores (where $w$ is a positive integer parameter)

@@

		\begin{algorithmic}[1]
		\Require{$v$ a binary array of length $n = c\cdot l$, $W$ the binary weight matrix representing the network}
		\Procedure{Sum of sum}{$v, W, \gamma, S, w$}
		%\Statex
		\For{$s$ from $1$ to S}
		\State $s \gets \gamma v + W v$
		\For{$i$ from $1$ to $c$}
			\Let{treshold}{Select(s[$i$], $w$)} \Comment{Select(t, w) returns the element that would be in rank $w$ if the array t was sorted}
			\For{$j$ from $1$ to $l$}
			\Let{$v[i][j]$}{$s[i][j]$ $\ge$ treshold}
			\EndFor
		\EndFor
		\EndFor
		%\State\Return v
		\EndProcedure
		\end{algorithmic}
		\end{algorithm}

@@

	As information is shared accross connections with multiple activated neurons per cluster, they are more resilient to network damages (for one message information is carried by $a^2 {c \choose 2}$ edges. $v_c$ will indicate a correct neuron that should be activated, $v$ the other type of neurons.

	Our deviation model is drawn from \cite{LedGriRabGro20145}\footnote{Compared to this article, we do not draw at random a letter in case of ambiguity, which hurts performance a bit.}.

	$P(n_{v_c} = x + \gamma ) = {a (c_k-1) \choose x} (1-\psi)^{x} \psi ^ { a (c - c_e -1) - x }$

	$P(n_{v_c} = x) = {a c_k \choose x} (1-\psi)^{x} \psi ^ { a (c - c_e) - x }$

@@

	\begin{figure}[!htb]

@@

	Figure \ref{comppsi} seems to indicate a linear relationship (after a transition for multiple activities) between $\eta_\psi -\eta_0$ and $\psi$.
	\section{Maximum theoretical efficiency}
		It was shown in \cite{oo}, asymptotic capacities of clique networks is $\log 2$. We generalise this result to multipartite cliques.

		The entropy of the messages set can be approximated as $H(\mathcal{M}) \approx m c \log_2 {l \choose a}$. From $d = 1 - \left (1- \left(\frac{a}{l}\right)^2 \right)^m$, we can deduce $m \sim \frac{\log_2(1-d)}{\log_2(1-(\frac{a}{l})^2)} \sim - \frac{l^2 \log_2(1-d) \log 2}{a^2}$.
		We set $\log_2 {l \choose a} = k c$ (otherwise density approaches $0$ or $1$, and efficiency $0$). It follows that $\eta \sim c \log_2 {l \choose a} \log2(1-d) \sim \frac{k c^2 \log_2(1-d)\log 2}{a^2 {c \choose 2}}$.

@@

	\nocite{*}
	\bibliographystyle{numeric} % Le style est mis entre crochets.
         \bibliography{bibli}
\end{document}
